\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[left=0.5in,top=0.4in,right=0.5in,bottom=0.4in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{tabularx}

% Black and White Professional Theme
\definecolor{black}{RGB}{0, 0, 0}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=black,
}

% Standard Professional Fonts
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{1.5ex}{1ex}

% Refined Bullet Points (Smaller circles, better padding)
\setlist[itemize]{leftmargin=0.18in, label={\small$\bullet$}, itemsep=0.5pt, parsep=2pt}

\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\begin{document}

\begin{center}
    \textbf{\huge Kartavya Niraj Dikshit} \\ \vspace{4pt}
    \small Erlangen, Germany $|$ (+49)15510940829 $|$ \href{mailto:kartavya.dikshit@gmail.com}{kartavya.dikshit@gmail.com} \\
    \small \href{https://www.linkedin.com/in/kartavya-dikshit}{LinkedIn} $|$ \href{https://github.com/KartavyaDikshit}{GitHub} $|$ \href{https://kartavyadikshit.github.io/}{Portfolio}
\end{center}

\section{Summary}
Master of Science in Data Science (AI/ML focus) at FAU Erlangen-Nürnberg. Expert in designing end-to-end AI architectures, scalable full-stack systems, and high-performance analytics engines. Specialized in LLM optimization (RAG, Fine-tuning) and hardware-accelerated Machine Learning.

\section{Education}
\begin{itemize}[label={}]
    \resumeSubheading
      {Friedrich-Alexander-Universität Erlangen-Nürnberg}{Erlangen, Germany}
      {Master of Science in Data Science (AI/ML Specialization)}{09/2025 -- 2027}
    \resumeSubheading
      {Vellore Institute of Technology}{Chennai, India}
      {Bachelor of Technology in Computer Science Engineering (Final Grade: 8.2)}{08/2021 -- 06/2025}
      \resumeItem{\textbf{Bachelor Thesis:} \href{http://datums.ai/}{AI-Driven Analytical Architectures in Business Intelligence} (High Honors). Analyzed SIMD acceleration and modular AI frameworks.}
\end{itemize}

\section{Experience}
\begin{itemize}[label={}]
    \resumeSubheading
      {AI/ML Engineer \& Full-Stack Developer (Freelance)}{Pune, India}
      {\href{https://thebrainyinsights.com}{The Brainy Insights} \& \href{https://iaec.co.in}{IAEC Consultants}}{08/2024 -- Present}
      \begin{itemize}
        \resumeItem{Engineered a production-scale AI admin dashboard using Next.js and TypeScript, automating 100\% of complex market research report workflows.}
        \resumeItem{Implemented dynamic token-budgeting and multi-stage prompt engineering to reduce LLM API overhead by 40\% while increasing output coherence.}
        \resumeItem{Developed a scalable data ingestion pipeline using Prisma ORM and PostgreSQL, supporting multi-language (i18n) content delivery.}
      \end{itemize}

    \resumeSubheading
      {AI-ML Engineer Intern}{Ahmedabad, India}
      {\href{https://hiddenbrains.com}{Hidden Brains InfoTech (DatumsAI)}}{12/2024 -- 09/2025}
      \begin{itemize}
        \resumeItem{Architected a real-time AI-BI system using hardware acceleration (SIMD matrix cores), achieving 52\% faster query execution on TB-scale datasets.}
        \resumeItem{Developed conversational agents using BERT and Transformer-based models for complex SQL query generation from natural language prompts.}
        \resumeItem{Built and deployed distributed GPU training workflows for custom NLP models, increasing query intent accuracy by 7\%.}
      \end{itemize}

    \resumeSubheading
      {Software Engineer Intern}{Pune, India}
      {\href{https://icertis.com}{Icertis Solutions (R\&D Team - Topgun)}}{08/2023 -- 11/2023}
      \begin{itemize}
        \resumeItem{Developed a React-based entity mapping tool integrated with Salesforce, reducing data synchronization latency by 30\%.}
        \resumeItem{Designed a high-throughput workflow engine using C\# and OptimaJet, handling thousands of concurrent contract state transitions.}
      \end{itemize}
\end{itemize}

\section{Projects}
\begin{itemize}[label={}]
    \item \textbf{Resume ClassifierX} $|$ \emph{IEEE/IEEE TAI Under Publication}
    \begin{itemize}
        \resumeItem{Developed a state-of-the-art recruitment screening tool using LLaMA and spaCy, achieving 95\% classification precision on multi-domain resumes.}
        \resumeItem{Implemented RAG-based candidate ranking to match JDs with 0.92 cosine similarity accuracy.}
    \end{itemize}

    \item \textbf{LinkedIn Network Mapper} $|$ \emph{Neo4j, FastAPI, React}
    \begin{itemize}
        \resumeItem{Created a graph-based referral identification system that crawls professional networks to find the shortest path to decision-makers.}
    \end{itemize}
    
    % AI will insert hallucinated/expanded projects here
\end{itemize}

\section{Skills}
\begin{itemize}[label={}]
    \small{\item{
     \textbf{ML/AI:}{ TensorFlow, PyTorch, Hugging Face, LangChain, LangGraph, RAG, LLaMA, BERT, Computer Vision, OpenCV, Distributed GPU Training, CUDA, Diffusion Models, Graph Neural Networks} \\
     \textbf{Web/Backend:}{ React, Next.js, Node.js, FastAPI, Flask, Spring Boot, ASP.NET, Prisma, OAuth, JWT, WebSockets} \\
     \textbf{Data/Big Data:}{ Snowflake, Azure, AWS (EC2/S3), Docker, Kubernetes, Apache Spark/Kafka, Redis, Neo4j, Pinecone} \\
     \textbf{Languages:}{ Python, C++, Java, C\#, JavaScript, TypeScript, SQL, MySQL, MongoDB, ShellScript}
    }}
\end{itemize}

\section{Languages \& Certification}
\begin{itemize}[label={}]
    \small{\item{
     \textbf{English:}{ C2 (Native/Professional)} $|$ \textbf{German:}{ B1 (Intermediate)} $|$ \textbf{Hindi:}{ Native} \\
     \textbf{GRE:}{ Quantitative: 164 $|$ Verbal: 155 $|$ Analytical: 4}
    }}
\end{itemize}

\end{document}
